Growth model analysis 3spp WB

### 2018-10-24 manuscriptAnalysis/MS_Analysis_3spp_WB.Rmd
added projOut, p/phi summaries

  phi <- array2df(ddD$q50$phiBetaInt, label.x = "est") %>%
    rename(est=est,isYOY=d1,species=d2,season=d3,river=d4,year=d5) %>% filter(river == 1) 
  ggplot(phi, aes(year,invlogit(est),color=factor(species))) +geom_point() + facet_grid( season ~ isYOY)

@@

@@

projOut <- list(stats3Spp, lm, relImp, anov, elapsed, simData)
save( projOut, file = 'D:/projects/linkedModels/data/out/projectionOut.RData')

@@

@@

#  ggsave(paste0('figures/3Spp_WB/relImpOcc',occSelected,'.png'), width = 9, height = 7, units='in')

@@

# leaving out bkt*bnt, too small
ggplot(rIAll, aes((occ), value, color = factor(rowname))) +
  geom_point() +
  geom_line() +
  geom_vline(xintercept = 3.5) +
  scale_x_continuous('Sampling occasion',
                    breaks = 2:10,
                    labels = c('Winter','Spring','Summer', 'Autumn','Winter','Spring','Summer', 'Autumn','Winter')
                    ) +
  scale_y_continuous('Relative proportion of variance explained') +
  theme_publication() +
  theme(axis.text.x  = element_text(angle=90, vjust=0.25, size=10)) +
  facet_wrap(~ var, labeller=labeller(var = labels))

@@

dodge <- position_dodge(width=0.9)
ggplot(rIMeans %>% filter(rowname %in% c('bktRI','bntRI')), aes(factor(var),mean, fill = factor(rowname, levels = c('bktRI','bntRI','atsRI'), ordered = TRUE))) +
  geom_errorbar(aes(ymin = mean-0.01, ymax = up), width = 0.25, position=dodge) +
  geom_col(position=dodge) +
  scale_x_discrete('Parameter',
                   labels = c('1' = 'Temp','2' = 'Flow','3' = 'Bkt','4' = 'Bnt','5' = 'Ats','6' = 'Temp*Flow', '7' = "Bkt*Bnt")) +
  scale_fill_grey() +
  scale_y_continuous('Relative proportion of variance explained') +
  theme_publication() +
  theme( legend.position = 'none')

@@

>>>>

  p %>% group_by(species) %>%
    summarize(meanP = mean(invlogit(est)),
              sdP = sd(invlogit(est)))

  p %>% group_by(season) %>%
    summarize(meanP = mean(invlogit(est)))

  ##################### 
  phi <- array2df(ddD$q50$phiBetaInt, label.x = "est") %>%
    rename(est=est,isYOY=d1,species=d2,season=d3,river=d4,year=d5) %>% filter(river == 1) 
  ggplot(phi, aes(year,invlogit(est),color=factor(species))) +geom_point() + facet_grid( season ~ isYOY)

@@

  phi %>% group_by(species) %>%
    summarize(meanPhi = mean(invlogit(est)),
              sdPhi = sd(invlogit(est)))

  phi %>% group_by(season) %>%
    summarize(meanPhi = mean(invlogit(est)))

@@

#projOut <- list(stats3Spp, lm, relImp, anov, elapsed, simData)
save( stats3Spp, lm, relImp, anov, elapsed, simData, file = 'D:/projects/linkedModels/data/out/projectionOut.RData')

@@

# temporary while projOut is a list
#stats3Spp <- projOut[[1]]
#simData <- projOut[[6]]

@@

  ggsave(paste0('figures/3Spp_WB/relImpOcc',occSelected,'.png'), width = 9, height = 7, units='in')

@@

# leaving out bkt*bnt, too small
ggplot(rIAll %>% filter(rowname %in% c('bktRI','bntRI')), aes((occ), value, color = factor(rowname))) +
  geom_point() +
  geom_line() +
  geom_vline(xintercept = 3.5) +
  scale_x_continuous('Sampling occasion',
                    breaks = 2:10,
                    labels = c('Winter','Spring','Summer', 'Autumn','Winter','Spring','Summer', 'Autumn','Winter')
                    ) +
  scale_y_continuous('Relative proportion of variance explained') +
  theme_publication() +
  theme(axis.text.x  = element_text(angle=90, vjust=0.25, size=10)) +
  facet_wrap(~ var, labeller=labeller(var = labels))

@@

dodge <- position_dodge(width=0.9)
ggplot(rIMeans %>% filter(rowname %in% c('bktRI','bntRI')), aes(factor(var),mean, fill = factor(rowname, levels = c('bktRI','bntRI','atsRI'), ordered = TRUE))) +
  geom_errorbar(aes(ymin = mean-0.01, ymax = up), width = 0.25, position=dodge) +
  geom_col(position=dodge) +
  scale_x_discrete('Parameter',
                   labels = c('1' = 'Temperature','2' = 'Flow','3' = 'Bkt','4' = 'Bnt','5' = 'Ats','6' = 'Temp*Flow', '7' = "Bkt*Bnt")) +
  scale_fill_grey() +
  scale_y_continuous('Relative proportion of variance explained') +
  theme_publication() +
  theme( legend.position = 'none')

@@

# mean rel Imp for env vs spp variables
rIMeans %>%
  mutate(isEnvVar = ifelse(var %in% c(1,2,6), 1,0)) %>%
  group_by(rowname,isEnvVar) %>%
  summarize(meanMean = mean(mean),
            sumMean = sum(mean),
            sdMean = sd(mean))

# ratio of env/(env+spp) means
.247/(.246+.0648) # bkt
.122/(.122+.159) # bnt

# ratio of env/(env+spp) sums - donT need to do ratio, just use sum for env
.635/.259 # den-dep bnt/bkt
.741/.365 # env bkt/bnt
